\documentclass[11pt]{article}

\usepackage[letterpaper]{geometry}

\usepackage{latexsym}
\usepackage{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{etaremune}
\usepackage{longtable}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%



\begin{document}
\pagestyle{plain}
\lhead{Kong Jan. 2020}

\begin{center}
\huge \textbf{Sungsik Kong}\\
\large Department of Evolution, Ecology \\
and Organismal Biology\\
\large The Ohio State University\\
\large 375 Jennings Hall \& 356 Aronoff Laboratory\\
\end{center}

\section*{Education}

\begin{longtable}{p{0.15\textwidth}  p{0.1\textwidth} p{0.52\textwidth} p{0.23\textwidth}}
2018 - Present & Ph.D. & Evolution, Ecology, and Organismal Biology & The Ohio State University\\
 & & Advisor: Dr. Laura Kubatko\\
2013 - 2015 & {M.Sc.} & Ecology and Evolutionary Biology & University of Toronto\\
 & & Advisor: Dr. Robert Murphy\\
2006 - 2012 & {B.Sc.} & Ecology and Evolutionary Biology and Zoology & University of Toronto\\
 & & Advisors: Drs. Deborah McLennan and Robert Murphy
\end{longtable}

\hspace{0pt}

\section*{Publications}
\subsection*{Peer-reviewed Journal Articles}
$^\ddag$Co-correspondence; $^\dag$Equal contribution
\begin{etaremune}

\item \textbf{Kong S} and Kubatko L. (2021) Comparative performance of popular methods for hybrid detection using genomic data. \textit {Systematic Biology} doi: \href{10.1093/sysbio/syaa092}10.1093/sysbio/syaa092

\item  Sánchez-Pacheco S{$^\ddag$}, \textbf{Kong S}{$^\ddag$}, Pulido-Santacruz P, Murphy RW, and Kubatko L. (2020) Median-joining network analysis of SARS-CoV-2 genomes is neither phylogenetic nor evolutionary. \textit{Proc. Natl. Acad. Sci. U.S.A} doi: \href{https://doi.org/10.1073/pnas.2007062117}10.1073/pnas.2007062117
\item Kim M, Nguyen HQ, Yi Y, Ahn J, Kim YE, Jang S, Kim S, \textbf{Kong S}, and Borzée A. (2020) Policy recommendation on whaling, trade and watching of cetaceans in the Republic of Korea. \textit{Biodiversity Journal} 11: 255–258 doi: \href{https://doi.org/10.31396/Biodiv.Jour.2020.11.1.255.258}https://doi.org/10.31396/Biodiv.Jour.2020.11.1.255.258
\item Weiringa JG, Boot MR,  Dantas-Queiroz MV, Duckett D, Fonseca EM, Glon H, Hamilton N, \textbf{Kong S}, Lanna FM, Mattingly KZ, Parsons DJ, Smith ML, Stone BW, Thompson C, Zuo L, and Carstens BC. (2020) Does habitat stability structure intraspecific genetic diversity? It’s complicated… \textit{Frontiers in Biogeography} e45377 doi:\href{https://doi.org/10.21425/F5FBG45377}10.21425/F5FBG45377
\item Borzée A, Purevdorj Z, Kim YI, \textbf{Kong S}, Choe M, Yi Y, Kim K, Kim A, and Jang Y. (2020) Breeding preferences in the Treefrogs \textit{Dryophytes japonicus} (Hylidae) in Mongolia, the northern limit of their range. \textit{Journal of Natural History} 53: 2685-2698 doi:\href{10.1080/00222933.2019.1704458}10.1080/00222933.2019.1704458
\item Groffen J, \textbf{Kong S}, Jang Y, and Borzée A. (2019) The invasive American bullfrog (\textit{Lithobates catesbeianus}) in the Republic of Korea: history and recommendation for population control. \textit{Management of Biological Invasions} 10:3 517–535 doi: \href{10.3391/mbi.2019.10.3.08}10.3391/mbi.2019.10.3.08
\item Bae Y, \textbf{Kong S}, Yi Y, Jang Y, and Borzée A. (2019) Additional new type of threat to \textit{Hynobius} salamander eggs: predation by loaches (\textit{Misgurnus} sp.) in agricultural wetlands. \textit{Animal Biology} 69:4 451–461 doi: \href{https://doi.org/10.1163/15707563-20191070}10.1163/15707563-20191070
\item Borzée A,\textbf{ Kong S}, Didinger C, Nguyen HQ, and Jang Y. (2018) A ring-species or a ring of species? Phylogenetic relationship between two treefrog species around the Yellow Sea: \textit{Dryophytes suweonensis }and \textit{D. immaculatus}. \textit{The Herpetological Journal} 28: 160–170 
\item Kim K, \textbf{Kong S}, Kim YI, Borzée A, Bae Y, and Jang Y. (2018) Japanese hard ticks (\textit{Ixodes nipponensis}) parasitizing on the endangered leopard cat (\textit{Prionaliurus bengalensis euptilura}) in the Republic of Korea. \textit{Animal Systematics, Evolution and Diversity} 34:1 23–26 doi: \href{10.5635/ASED.2018.34.1.032}10.5635/ASED.2018.34.1.032
\item \textbf{Kong S}{$^\dag$}, Sánchez-Pacheco S{$^\dag$}, and Murphy RW. (2016) On the use of Median-Joining Networks in evolutionary biology. \textit{Cladistics} 32: 691–699 doi: \href{https://doi.org/10.1111/cla.12147}10.1111/cla.12147

\end{etaremune}


\hspace{0pt}

\section*{Presentations}

\begin{longtable}{p{0.1\textwidth}  p{0.9\textwidth}}
2021 & \textbf{Talk}  EEOB Recruitment Speed Talk, The Ohio State University, OH., USA. \textit{High performance computing environment at the Ohio State University.}\\ 
2021 & \textbf{Talk}  EEOB Annual Darwin Series, The Ohio State University, OH., USA. \textit{Comparative performance of popular methods for hybrid detection using genomic data.}\\ 
2020 & \textbf{Talk}  E\&E Club, The Ohio State University, OH., USA. \textit{Which tool to use to detect hybridization?}\\ 
2020 & \textbf{Talk}  SSB Meeting, Gainesville, FL., USA. \textit{Comparison and evaluation on the accuracy of popular hybrid detection methods using simulated data.}\\ 
2019 & \textbf{Talk}  E\&E Club, The Ohio State University, OH., USA. \textit{The giving tree: how the branching pattern of a tree is used in evolutionary biology.}\\
2019 &  \textbf{Poster} Evolution, Providence, RI., USA. \textit{Performance and accuracy of Median-Joining Networks and comparisons with bayesian phylogenies.}\\  
2019 & \textbf{Invited Talk} The Stone Laboratory: EEOB 1930, Gibraltar Island, OH., USA. \textit{Phylogenetic networks and behavioral evolution of Primates.}\\
2019 & \textbf{Poster} The Ohio State University Department of EEOB Recruitment weekend \textit{My first year of Ph.D. experience at the Ohio State University.}\\
2017 & \textbf{Poster} Annual Conference of the Korean Association of Biological Sciences, Yongin, South Korea. \textit{Performance and accuracy of Median-Joining Networks and comparisons with bayesian phylogenies.}\\
2017 & \textbf{Talk} Ewha Womans University Animal Communication Symposium, Seoul, South Korea. \textit{Illustrating hybridization.}\\
2016 & \textbf{Invited Talk} Ewha Womans University Eco-science/Eco-creative seminar for graduate students, Seoul, South Korea. \textit{On the use of Median-Joining network.}\\
2014 & \textbf{Poster} Korean-American Scientists and Engineers Association (KSEA) Young Generation Technical and Leadership Conference (YGTLC), Houston, TX., USA. \textit{Matrilineal relationships of green pitvipers with the description of a new species of the genus} Trimeresurus \textit{(Squamata: Viperidae: Crotalinae) from the central highlands of Vietnam.}\\
2013 & \textbf{Talk} Ewha Womans’ University, Laboratory of Behavior and Ecology Weekly Seminar, Seoul, South Korea. \textit{The evolution of infanticide and male takeover in primates in a macro-evolutionary framework.}\\
2012 & \textbf{Poster} University of Toronto Ecology and Evolutionary Biology Undergraduate Research Fair, Toronto, ON., Canada. \textit{The evolution of infanticide and male takeover in primates in a macro-evolutionary framework.}\\
\end{longtable}

\hspace{0pt}

\pagebreak
\section*{Students advising}

\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}

2021--Present & \textbf{Mentor} Woodsworth Mentorship Program, University of Toronto, Canada\\
		       &Mentee: Alanna Kong, University of Toronto (2021-2022)\\
2019--Present & \textbf{Mentor} Department of EEOB Graduate Mentoring, The Ohio State University, OH., USA \\
		       &Mentee: McKenna Molnar, The Ohio State University (2020-2021)\\
2020--Present& \textbf{Mentor} Graduate Student Mentorship Initiative Mentor, Científico Latino\\
			&Mentee: Devansh Pandey (2021-2022)\\

2020 Summer&Shelby Jansens and Kimberly Wiles, co-advised with Dr. Laura Kubatko, MBI REU program. \textit{Detecting shifts in the evolutionary process in SARS-CoV-2 genomes.}\\
2015 Spring&Tulio Soares and Ellen Southam, University of Toronto and Royal Ontario Museum. \textit{On the use of Median-Joining Networks: A philosophical and empirical evaluation of its suitability in evolutionary biology.}\\
2014 Summer&Shreeram Senthivasan, University of Toronto and Royal Ontario Museum. \textit{Matrilineal relationships of green pitvipers with the description of a new species of the genus} Trimeresurus \textit{(Squamata: Viperidae: Crotalinae) from the central highlands of Vietnam.}

\end{longtable}

\hspace{-1pt}
\section*{Teaching Experiences}

\subsection*{Teaching Assistantship}

\textit{The Ohio State University}\\
\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}

2021 Fall & \textit{EEOB 3310} Evolution\\
2021 Summer & \textit{EEOB 2520} Human Physiology\\
2021 Spring & \textit{EEOB 3310} Evolution\\
2020 Fall & \textit{EEOB 3310} Evolution\\
2020 Summer & \textit{EEOB 3310} Evolution\\
2020 Spring & \textit{EEOB 3310} Evolution\\
2019 Fall & \textit{EEOB 3310} Evolution\\
2019 Summer & \textit{EEOB 1930} Introduction to Biological Studies--Aquatic Biology\\
2019 Spring & \textit{EEOB 3310} Evolution\\
2018 Fall & \textit{BIOL 1113} Energy Transformation and Development\\
\end{longtable}


\textit{University of Toronto}\\
\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}

2015 Summer  & \textit{BIO 120} Adaptation and Biodiversity\\
2015 Spring & \textit{BIO 220} From Genomics to Ecosystems in a Changing World\\
2014 Fall & \textit{EEB 362} Macroevolution\\
2014 Summer & \textit{BIO 120} Adaptation and Biodiversity\\
2014 Spring & \textit{EEB 386} Avian Biology\\
2013 Fall & \textit{BIO 120} Adaptation and Biodiversity\\

\end{longtable}








%-------------------------------------------
\end{document}