\documentclass[10pt]{article}

\usepackage[a4paper, total={6in, 8in}]{geometry}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{etaremune}
\usepackage{longtable}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting



%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%



\begin{document}
\pagestyle{plain}
\lhead{Kong Jan. 2020}

\begin{center}
\huge \textbf{Sungsik Kong}\\
\large Department of Evolution, Ecology \\
and Organismal Biology\\
\large The Ohio State University\\
\large 375 Jennings Hall \& 356 Aronoff Laboratory\\
\small \href{http://minglabaaa.github.io}http://minglabaaa.github.io/\\
\small \href{mailto:sungsik.kong@gmail.com}sungsik.kong@gmail.com
\end{center}

\section*{Education}

\begin{longtable}{p{0.15\textwidth}  p{0.1\textwidth} p{0.52\textwidth} p{0.23\textwidth}}
2018 -   & Ph.D. & Evolution, Ecology, and Organismal Biology & The Ohio State University\\
 & & Advisor: Dr. Laura Kubatko\\
2013 - 2015 & {M.Sc.} & Ecology and Evolutionary Biology & University of Toronto\\
 & & Advisor: Dr. Robert Murphy\\
2006 - 2012 & {B.Sc.} & Ecology and Evolutionary Biology and Zoology & University of Toronto\\
 & & Advisor: Drs. Deborah McLennan and Robert Murphy\\
\end{longtable}



\section*{Publications}
\subsection*{Peer-reviewed Journal Articles}
$^\ddag$Co-correspondence; $^\dag$Equal contribution
\begin{etaremune}

\item  Sánchez-Pacheco S{$^\ddag$}, \textbf{Kong S}{$^\ddag$}, Pulido-Santacruz P, Murphy RW, and Kubatko L. (2020) Median-joining network analysis of SARS-CoV-2 genomes is neither phylogenetic nor evolutionary \textit{Proc. Natl. Acad. Sci. U.S.A} doi: \href{https://doi.org/10.1073/pnas.2007062117}10.1073/pnas.2007062117
\item Weiringa JG, Boot MR,  Dantas-Queiroz MV, Duckett D, Fonseca EM, Glon H, Hamilton N, \textbf{Kong S}, Lanna FM, Mattingly KZ, Parsons DJ, Smith ML, Stone BW, Thompson C, Zuo L, Carstens BC. (2020) Does habitat stability structure intraspecific genetic diversity? It’s complicated… \textit{Frontiers in Biogeography} e45377 doi:\href{https://doi.org/10.21425/F5FBG45377}10.21425/F5FBG45377
\item Borzée A, Purevdorj Z, Kim YI, \textbf{Kong S}, Choe M, Yi Y, Kim K, Kim A, Jang Y. (2020) Breeding preferences in the Treefrogs \textit{Dryophytes japonicus} (Hylidae) in Mongolia, the northern limit of their range. \textit{Journal of Natural History} 53: 2685-2698 doi:\href{10.1080/00222933.2019.1704458}10.1080/00222933.2019.1704458
\item Groffen J, \textbf{Kong S}, Jang Y, Borzée A. (2019) The invasive American bullfrog (\textit{Lithobates catesbeianus}) in the Republic of Korea: history and recommendation for population control. \textit{Management of Biological Invasions} 10:3 517–535 doi: \href{10.3391/mbi.2019.10.3.08}10.3391/mbi.2019.10.3.08
\item Bae Y, \textbf{Kong S}, Yi Y, Jang Y, Borzée A. (2019) Additional new type of threat to \textit{Hynobius} salamander eggs: predation by loaches (\textit{Misgurnus} sp.) in agricultural wetlands. \textit{Animal Biology} 69:4 451–461 doi: \href{https://doi.org/10.1163/15707563-20191070}10.1163/15707563-20191070
\item Borzée A,\textbf{ Kong S}, Didinger C, Nguyen HQ, Jang Y. (2018) A ring-species or a ring of species? Phylogenetic relationship between two treefrog species around the Yellow Sea: \textit{Dryophytes suweonensis }and \textit{D. immaculatus}. \textit{The Herpetological Journal} 28: 160–170 
\item Kim K, \textbf{Kong S}, Kim YI, Borzée A, Bae Y, Jang Y. (2018) Japanese hard ticks (\textit{Ixodes nipponensis}) parasitizing on the endangered leopard cat (\textit{Prionaliurus bengalensis euptilura}) in the Republic of Korea. \textit{Animal Systematics, Evolution and Diversity} 34:1 23–26 doi: \href{10.5635/ASED.2018.34.1.032}10.5635/ASED.2018.34.1.032
\item \textbf{Kong S}{$^\dag$}, Sánchez-Pacheco S{$^\dag$} and Murphy RW. (2016) On the use of Median-Joining Networks in evolutionary biology. \textit{Cladistics} 32: 691–699 doi: \href{https://doi.org/10.1111/cla.12147}10.1111/cla.12147

\end{etaremune}

\subsection*{Policy Recommendations}
\begin{etaremune}

\item Kim M, Nguyen HQ, Yi Y, Ahn J, Kim YE, Jang S, Kim S, \textbf{Kong S}, Borzée A. (2020) Policy recommendation on whaling, trade and watching of cetaceans in the Republic of Korea. \textit{Biodiversity Journal} 11: 255–258 doi: \href{https://doi.org/10.31396/Biodiv.Jour.2020.11.1.255.258}https://doi.org/10.31396/Biodiv.Jour.2020.11.1.255.258
\item Borzée A, Nguyen HQ, Ahn J, Kim M, Kim S, Jang S, \textbf{Kong S}, Kim YE, Yi Y. (2017) Policy recommendation on the negative impact of infrastructure development on the population of endangered Long-Tailed Goral in Oseck-Kkeutchong. \textit{Society for Conservation Biology Korean Chapter}

\end{etaremune}



\section*{Presentations}

\begin{longtable}{p{0.1\textwidth}  p{0.9\textwidth}}
2020 & \textbf{Talk}  E\&E Club, The Ohio State University, OH., USA. \textit{Which tool to use to detect hybridization?}\\ 
2020 & \textbf{Talk}  SSB Meeting, Gainesville, FL., USA. \textit{Comparison and evaluation on the accuracy of popular hybrid detection methods using simulated data.}\\ 
2019 & \textbf{Talk}  E\&E Club, The Ohio State University, OH., USA. \textit{The giving tree: how the branching pattern of a tree is used in evolutionary biology.}\\
2019 &  \textbf{Poster} Evolution, Providence, RI., USA. \textit{Performance and accuracy of Median-Joining Networks and comparisons with bayesian phylogenies.}\\  
2019 & \textbf{Invited Talk} The Stone Laboratory: EEOB 1930, Gibraltar Island, OH., USA. \textit{Phylogenetic networks and behavioral evolution of Primates.}\\
2019 & \textbf{Poster} The Ohio State University Department of EEOB Recruitment weekend \textit{My first year of Ph.D. experience at the Ohio State University.}\\
2017 & \textbf{Poster} Annual Conference of the Korean Association of Biological Sciences, Yongin, South Korea. \textit{Performance and accuracy of Median-Joining Networks and comparisons with bayesian phylogenies.}\\
2017 & \textbf{Talk} Ewha Womans University Animal Communication Symposium, Seoul, South Korea. \textit{Illustrating hybridization.}\\
2016 & \textbf{Invited Talk} Ewha Womans University Eco-science/Eco-creative seminar for graduate students, Seoul, South Korea. \textit{On the use of Median-Joining Network.}\\
2014 & \textbf{Poster} Korean-American Scientists and Engineers Association (KSEA) Young Generation Technical and Leadership Conference (YGTLC), Houston, TX., USA. \textit{Matrilineal relationships of green pitvipers with the description of a new species of the genus} Trimeresurus \textit{(Squamata: Viperidae: Crotalinae) from the central highlands of Vietnam.}\\
2013 & \textbf{Talk} Ewha Womans’ University, Laboratory of Behavior and Ecology Weekly Seminar, Seoul, South Korea. \textit{The evolution of infanticide and male takeover in primates in a macro-evolutionary framework.}\\
2012 & \textbf{Poster} University of Toronto Ecology and Evolutionary Biology Undergraduate Research Fair, Toronto, ON., Canada. \textit{The evolution of infanticide and male takeover in primates in a macro-evolutionary framework.}\\
\end{longtable}

\section*{Additional Academic Experiences}

\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}

2020 &	\textbf{Invited Guest} TDAI Kickoff Event, College of Arts and Sciences, the Ohio State University, Columbus, OH., USA\\
2020 &	\textbf{Participant} Future of Systematics Workshop, SSB Meeting, funded by NSF, hosted by Dr. Emily Sessa, University of Florida, Gainesville, FL., USA\\
2020 &	\textbf{Participant} SSB Meeting, Gainesville, FL., USA\\
2019 &  \textbf{Participant} Evolution, Providence, RI., USA\\
2019 &	\textbf{Participant} Midwest Phylogenetics Workshop, Itasca Biological Station, funded by NSF, hosted by Dr. Emma Goldberg, University of Minnesota, MN., USA\\
2019 & \textbf{Volunteer} Museum of Biological Diversity’s Open House, the Ohio State University, OH., USA\\
2017 &	\textbf{Participant} Society for Conservation Biology (SCB) Asia Section Workshop on Conservation policy, funded and hosted by SCB, Bangkok, Thailand\\
2016 - 2017 & \textbf{Researcher} with Dr. Yikweon Jang, Ewha Womans University, Division of Ecoscience, Seoul, South Korea\\
2016 - 2017 &	\textbf{Communication Officer} Society for Conservation Biology, Korean Chapter, South Korea\\
2016 &	\textbf{Researcher} Konkuk University, School of Medicine, Seoul, South Korea\\
2016 &	\textbf{Participant} World Congress of Herpetology, Hangzhou and Tonglu, China\\
2016 &	\textbf{Volunteer} Kuang Si Butterfly Park, Luang Prabang, Laos\\
2015 &	\textbf{Participant} Phylogenomics Symposium and Software School, funded by NSF, hosted by Dr. Tandy Warnow (University of Illinois at Urbana-Champaign), University of Michigan, Ann Arbor, MI., USA\\
2015 &	\textbf{Participant} Society for Systematic Biologists (SSB) Meeting, Ann Arbor, MI., USA\\
2013 &	\textbf{Researcher} with Dr. Jae Chun Choe, Ewha Womans University, Division of Ecoscience, Seoul, South Korea\\
2012 &	\textbf{Student Researcher} with Dr. Robert Murphy, Centre for Biodiversity and Conservation Biology, Royal Ontario Museum, Toronto, ON., Canada\\
2011 - 2013 &	\textbf{Biodiversity Technician} with Eric Davies, Urban Biodiversity and Forestry Laboratory, University of Toronto, ON., Canada\\
2011 - 2012 &	\textbf{Student Researcher} with Dr. Deborah McLennan, McLennan Laboratory, University of Toronto, Canada\\
2011 - 2011&	\textbf{Work-Study Student} Wildlife Ecology Laboratory, University of Toronto, Canada\\
2010 & \textbf{Field Research Assistant} Cities Centre, University of Toronto, Canada\\

\end{longtable}

\subsection*{Students advising}

\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}

2020 Summer&Shelby Jansens and Kimberly Wiles, co-advised with Dr. Laura Kubatko, MBI REU program\\

\end{longtable}


\section*{Grants and Awards}

\begin{longtable}{p{0.15\textwidth}  p{0.8\textwidth} p{0.05\textwidth}}

2020 &	SSE Graduate Research Excellence Grant (GREG) – R.C. Lewontin Award competition & \$1800\\
2020 &	Ray Travel Award for Service and Scholarship, the Ohio State University & Unfunded\\
2019 &	Ray Travel Award for Service and Scholarship, the Ohio State University & Unfunded\\
2014 &	E.M. Walker Graduate Award in Biodiversity, University of Toronto & \$2615\\
2013 - 2014 & University of Toronto Fellowship &  \\
2011 &	University of Toronto Undergraduate Bursary & Funded\\

\end{longtable}



\section*{Professional Services}
\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}

2019 -  &	\textbf{Journal reviewer for}: \textit{Systematic Biology}, \textit{Frontiers of Biogeography}\\
2015 - &  \textbf{Society Memberships}: Society of Systematic Biologists, Society for Study of Evolution, American Society of Naturalists\\
2019 - 2020 &	Admissions Committee, Department of Evolution, Ecology and Organismal Biology, The Ohio State University, OH., USA\\
2020 - 2021 &  Graduate Studies Committee, Department of Evolution, Ecology and Organismal Biology, The Ohio State University, OH., USA


\end{longtable}


\section*{Teaching Experiences}
\textit{Courses taught}

\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}

2018 -  &	\textbf{Teaching Assistant} The Ohio State University\\
 & \textit{BIOL 1113} Energy Transformation and Development\\
& \textit{EEOB 3310} Evolution\\
& \textit{EEOB 1930} Introduction to Biological Studies - Aquatic Biology\\

\end{longtable}



\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}

2013 - 2015 & \textbf{Teaching Assistant} University of Toronto\\
 & \textit{BIO 120} Adaptation and Biodiversity\\
 & \textit{BIO 220} From Genomics to Ecosystems in a Changing World\\
& \textit{EEB 362} Macroevolution\\
& \textit{EEB 386} Avian Biology\\

\end{longtable}




\newpage

\section*{References}

\begin{enumerate}

\item Prof. Dr. Laura S. Kubatko\\Department of Statistics,\\Department of Evolution, Ecology, and Organismal Biology\\The Ohio State University,\\219 Cockins Hall,\\Columbus, OH., 43210, USA\\\href{lkubatko@stat.osu.edu}lkubatko@stat.osu.edu\\+1 614-247-8846\\

\item Prof. Dr. Robert W. Murphy\\Sr. Curator, Herpetology\\Centre for Biodiversity and Conservation Biology\\Department of Natural History-Royal Ontario Museum\\And Professor of Ecology and Evolutionary Biology\\ University of Toronto\\100 Queen’s Park\\Toronto, ON., M3S 2C6, Canada\\\href{bob.murphy@utoronto.ca}bob.murphy@utoronto.ca\\+1 416-586-8099

\item Prof. Dr. Deborah A. Mclennan\\Department of Ecology and Evolutionary Biology\\University of Toronto,\\25 Harbord St.\\Toronto, ON., M5S 3G5, Canada \\\href{deborah.mclennan@utoronto.ca}deborah.mclennan@utoronto.ca\\+1 416-978-8538
\end{enumerate}









%-------------------------------------------
\end{document}