\documentclass[11pt]{article}

\usepackage[letterpaper]{geometry}

\usepackage{latexsym}
\usepackage{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{etaremune}
\usepackage{longtable}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\The Ohio State
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%



\begin{document}
\pagestyle{plain}
\lhead{Kong Jan. 2020}

\begin{center}
\huge \textbf{Sungsik Kong}\\
\vspace{0.2cm}
\large Department of Evolution, Ecology and Organismal Biology\\
\large The Ohio State University\\
\large 400 Aronoff Laboratory\\
\small \href{http://minglabaaa.github.io}http://minglabaaa.github.io/\\
\small \href{mailto:sungsik.kong@gmail.com}sungsik.kong@gmail.com
\end{center}







\section*{Education}

\begin{longtable}{p{0.15\textwidth}  p{0.1\textwidth} p{0.52\textwidth} p{0.23\textwidth}}
2018--Present & \textbf{Ph.D.} & Evolution, Ecology, and Organismal Biology (EEOB) & The Ohio State University\\
 & & Advisor: Dr. Laura Kubatko\\
2013--2015 & \textbf{M.Sc.} & Ecology and Evolutionary Biology (EEB) & University of Toronto\\
 & & Advisor: Dr. Robert Murphy\\
2006--2012 & \textbf{B.Sc.} & Ecology and Evolutionary Biology and Zoology & University of Toronto\\
 & & Advisors: Drs. Deborah McLennan and Robert Murphy
\end{longtable}



\hspace{0pt}



\section*{Publications}
\subsection*{Manuscripts in Progress}
\begin{etaremune}

%Alec SHEETS; 
%Network Inference KONG; 
%Network Inference Software KONG;  
%Network Methods Comparison KONG; 
%One with Claudia
%One with Claudia
%One with Jeremy -- the teaching tool

	\item Glon MG, Broe MB, \textbf{Kong S}, Thoma RF, Crandall KA, Daly M and Freudenstein JV. (In preparation) Anchored Hybrid Enrichment Resolves the \textit{Lacunicambarus} (Decapoda: Cambaridae) Phylogeny.
	\item Glon H, Häussermann V, \textbf{Kong S}, Brewin P, Brickle P, and Daly M. (In preparation) The influence of deep historic and recent anthropogenic activities on the globalization of the plumose sea anemone, \textit{Metridium senile}.
	\item \textbf{Kong S}, Sánchez-Pacheco SJ, and Murphy RW. (In preparation) Topological Incongruence between Median-Joining Networks and Bayesian Inference Phylogenies.
	\item \textbf{Kong S}, Wicke K, Kubatko LS, and Pons JC. (In preparation) Classes of Phylogenetic Networks and their Mathematical and Biological Significance.
	\item Peng J, \textbf{Kong S} and Kubatko LS. (In preparation) A Likelihood Ratio Test for Hybridization Under the Multispecies Coalescent.
	\item Fu M, \textbf{Kong S}, Lamichhaney S, Eimes JA, and Waldman B. (In preparation) Adaptation of amphibian major histocompatibility genes to an emerging infectious disease.
\end{etaremune}



\subsection*{Peer-reviewed Journal Articles}
$^\ddag$Co-correspondence; $^\dag$Equal contribution
\begin{etaremune}

\item \textbf{Kong S} and Kubatko LS. (2021) Comparative performance of popular methods for hybrid detection using genomic data. \textit {Systematic Biology} doi: \href{10.1093/sysbio/syaa092}10.1093/sysbio/syaa092

\item  Sánchez-Pacheco SJ{$^\ddag$}, \textbf{Kong S}{$^\ddag$}, Pulido-Santacruz P, Murphy RW, and Kubatko L. (2020) Median-joining network analysis of SARS-CoV-2 genomes is neither phylogenetic nor evolutionary. \textit{Proc. Natl. Acad. Sci. U.S.A} doi: \href{https://doi.org/10.1073/pnas.2007062117}10.1073/pnas.2007062117
	
	\begin{itemize}\item In the 99th percentile of all research outputs tracked by Altmetric
				\item Scoring higher Altmetric Attention Score than 98\% of all research outputs of similar age \end{itemize}
	
\item Kim M, Nguyen HQ, Yi Y, Ahn J, Kim YE, Jang S, Kim S, \textbf{Kong S}, and Borzée A. (2020) Policy recommendation on whaling, trade and watching of cetaceans in the Republic of Korea. \textit{Biodiversity Journal} 11: 255–258 doi: \href{https://doi.org/10.31396/Biodiv.Jour.2020.11.1.255.258}https://doi.org/10.31396/Biodiv.Jour.2020.11.1.255.258
\item Weiringa JG, Boot MR,  Dantas-Queiroz MV, Duckett D, Fonseca EM, Glon H, Hamilton N, \textbf{Kong S}, Lanna FM, Mattingly KZ, Parsons DJ, Smith ML, Stone BW, Thompson C, Zuo L, and Carstens BC. (2020) Does habitat stability structure intraspecific genetic diversity? It’s complicated… \textit{Frontiers in Biogeography} e45377 doi:\href{https://doi.org/10.21425/F5FBG45377}10.21425/F5FBG45377
\item Borzée A, Purevdorj Z, Kim YI, \textbf{Kong S}, Choe M, Yi Y, Kim K, Kim A, and Jang Y. (2020) Breeding preferences in the Treefrogs \textit{Dryophytes japonicus} (Hylidae) in Mongolia, the northern limit of their range. \textit{Journal of Natural History} 53: 2685-2698 doi:\href{10.1080/00222933.2019.1704458}10.1080/00222933.2019.1704458
\item Groffen J, \textbf{Kong S}, Jang Y, and Borzée A. (2019) The invasive American bullfrog (\textit{Lithobates catesbeianus}) in the Republic of Korea: history and recommendation for population control. \textit{Management of Biological Invasions} 10:3 517–535 doi: \href{10.3391/mbi.2019.10.3.08}10.3391/mbi.2019.10.3.08
\item Bae Y, \textbf{Kong S}, Yi Y, Jang Y, and Borzée A. (2019) Additional new type of threat to \textit{Hynobius} salamander eggs: predation by loaches (\textit{Misgurnus} sp.) in agricultural wetlands. \textit{Animal Biology} 69:4 451–461 doi: \href{https://doi.org/10.1163/15707563-20191070}10.1163/15707563-20191070
\item Borzée A,\textbf{ Kong S}, Didinger C, Nguyen HQ, and Jang Y. (2018) A ring-species or a ring of species? Phylogenetic relationship between two treefrog species around the Yellow Sea: \textit{Dryophytes suweonensis }and \textit{D. immaculatus}. \textit{The Herpetological Journal} 28: 160–170 
\item Kim K, \textbf{Kong S}, Kim YI, Borzée A, Bae Y, and Jang Y. (2018) Japanese hard ticks (\textit{Ixodes nipponensis}) parasitizing on the endangered leopard cat (\textit{Prionaliurus bengalensis euptilura}) in the Republic of Korea. \textit{Animal Systematics, Evolution and Diversity} 34:1 23–26 doi: \href{10.5635/ASED.2018.34.1.032}10.5635/ASED.2018.34.1.032
\item \textbf{Kong S}{$^\dag$}, Sánchez-Pacheco S{$^\dag$}, and Murphy RW. (2016) On the use of Median-Joining Networks in evolutionary biology. \textit{Cladistics} 32: 691–699 doi: \href{https://doi.org/10.1111/cla.12147}10.1111/cla.12147

\end{etaremune}

\subsection*{Policy Recommendations}
\begin{etaremune}


\item Borzée A, Nguyen HQ, Ahn J, Kim M, Kim S, Jang S, \textbf{Kong S}, Kim YE, and Yi Y. (2017) Policy recommendation on the negative impact of infrastructure development on the population of endangered Long-Tailed Goral in Oseck-Kkeutchong. \textit{Society for Conservation Biology Korean Chapter}

\end{etaremune}

\subsection*{Other Writings for a Popular Audience}
\begin{etaremune}

\item \textbf{Kong S} (2019) The giving tree: how the branching pattern of a tree is used in evolutionary biology. Available on \href{http://eeobcourseblogwolfestudents.blogspot.com/2019/11/the-giving-tree-how-branching-pattern.html}http://eeobcourseblogwolfestudents.blogspot.com/2019/11/the-giving-tree-how-branching-pattern.html
\item \textbf{Kong S} and Fonseca  EM. (2019) So far and yet so similar: Convergent evolution in helicopter damselflies. Available on \href{https://minglabaaa.github.io/posts/2019/01/blog-post-1/}https://minglabaaa.github.io/posts/2019/01/blog-post-1/



\end{etaremune}

\hspace{0pt}











\section*{Presentations}

\subsection*{Invited Talks}

\begin{longtable}{p{0.1\textwidth}  p{0.9\textwidth}}


2021 & \textbf{Kong S} and Kubatko L.  ``Comparative performance of popular methods for hybrid detection using genomic data" Annual Conference of the Korean Association of Biological Sciences, Ewha Womans University, South Korea, virtual (Selected among participants) \vspace{10pt} \\ 

2021 & \textbf{Kong S} and Kubatko L.  ``Comparative performance of popular methods for hybrid detection using genomic data" Workshop in Mathematical and Computational Biology, virtual (Selected among 206 participants)\textit{} \vspace{10pt} \\ 

2021 & \textbf{Kong S} ``How my gap year changed my perspectives" Misericordia University, PA., USA, virtual \vspace{10pt} \\  

2021 & \textbf{Kong S} ``High performance computing environment at the Ohio State University" EEOB Recruitment Speed Talk, The Ohio State University, OH., USA, virtual \vspace{10pt} \\ 

2019 &  \textbf{Kong S} ``Phylogenetic networks and behavioral evolution of Primates" The Stone Laboratory, Gibraltar Island, OH., USA \vspace{10pt} \\ 

2016 & \textbf{Kong S} and Murphy RW. ``On the use of Median-Joining network" Ewha Womans University Eco-science/Eco-creative Graduate Seminar, Seoul, South Korea \vspace{10pt} \\

2013 & \textbf{Kong S} and McLennan DA. ``The evolution of infanticide and male takeover in primates in a macro-evolutionary framework" Laboratory of Behavior and Ecology Weekly Seminar, Ewha Womans’ University, Seoul, South Korea \vspace{10pt} \\ 
\end{longtable}

\subsection*{Regular Talks}
\begin{longtable}{p{0.1\textwidth}  p{0.9\textwidth}}
2021 & \textbf{Kong S} and Kubatko L.  ``Comparative performance of popular methods for hybrid detection using genomic data" Evolution Meeting, virtual \textit{} \vspace{10pt} \\ 




2021 & \textbf{Kong S} and Kubatko L.  ``Comparative performance of popular methods for hybrid detection using genomic data" EEOB Annual Darwin Series, The Ohio State University, OH., USA, virtual \vspace{10pt} \\ 
2020 & \textbf{Kong S} ``Which tool to use to detect hybridization?" Evolution \& Ecology (E\&E) Club, The Ohio State University, OH., USA \vspace{10pt} \\
2020 & \textbf{Kong S} and Kubatko L.  ``Comparison and evaluation on the accuracy of popular hybrid detection methods using simulated data" Society of Systematic Biologists (SSB) Standalone Meeting, Gainesville, FL., USA \vspace{10pt} \\ 
2019 &  \textbf{Kong S} ``The giving tree: how the branching pattern of a tree is used in evolutionary biology" E\&E Club, The Ohio State University, OH., USA \vspace{10pt} \\  

2017 & \textbf{Kong S} ``Illustrating hybridization" Animal Communication Symposium, Ewha Womans University, Seoul, South Korea \vspace{10pt} \\  

\end{longtable}



\subsection*{Posters}
\begin{longtable}{p{0.1\textwidth}  p{0.9\textwidth}}
2019 & \textbf{Kong S} and Murphy RW. ``Performance and accuracy of Median-Joining Networks and comparisons with bayesian phylogenies" Evolution Meeting, Providence, RI., USA \vspace{10pt} \\ 
2019 &  \textbf{Kong S} ``My first year of Ph.D. experience at The Ohio State University" EEOB Recruitment Weekend,  The Ohio State University, OH., USA\vspace{10pt} \\ 
2017 & \textbf{Kong S} and Murphy RW. ``Performance and accuracy of Median-Joining Networks and comparisons with bayesian phylogenies"  Annual Conference of the Korean Association of Biological Sciences, Yong-In, South Korea\vspace{10pt} \\ 
2014 & \textbf{Kong S} Lathrop A, and Murphy RW. ``Matrilineal relationships of green pitvipers with the description of a new species of the genus \textit{Trimeresurus} (Squamata: Viperidae: Crotalinae) from the central highlands of Vietnam" Korean-American Scientists and Engineers Association Young Generation Technical and Leadership Conference, Houston, TX., USA\vspace{10pt} \\ 
2012 & \textbf{Kong S} and McLennan DA. ``The evolution of infanticide and male takeover in primates in a macro-evolutionary framework" University of Toronto EEB Undergraduate Research Fair, Toronto, ON., Canada\vspace{10pt}\\
\end{longtable}


\subsection*{Contributed Presentations}
$^\dag$Presenter
\begin{longtable}{p{0.1\textwidth}  p{0.9\textwidth}}
2021 & Peng J$^\dag$, \textbf{Kong S}, and Kubatko L. ``A likelihood ratio test for hybridization under the multispecies coalescent" Faux-live talk, Evolution Meeting, virtual \vspace{10pt} \\ 
2018 & Kim YI$^\dag$, \textbf{Kong S}, Ha J, Borzée A, and Jang Y. ``Thermal tolerance variations in anuran larvae along a latitudinal gradient" Talk, Ecological Soceity of American Annual meeting, New Orleans, LA., USA \vspace{10pt} \\ 
2012 & Davies E$^\dag$, Eckenwalder J and He W. ``Trees of the temperate broadleaf forest biome"
Canadian urban forest conference, London, Ontario, Canada, Poster preparation \vspace{10pt} \\ 
2012 & Davies E$^\dag$. ``Native vs. Non native trees" Biodiversity \& Human Health Credit Valley Conservation Stewardship Forum, Powerpoint preparation \vspace{10pt} \\ 
\end{longtable}

\hspace{0pt}





\section*{Additional Academic Experiences}

\subsection*{Academic Service}
\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}
2019--Present &	\textbf{Journal reviewer for}: \textit{Systematic Biology}; \textit{Frontiers of Biogeography}; \textit{Infection, Genetics and Evolution};\\
2015--Present &  \textbf{Society Memberships}: Society of Systematic Biologists, Society for Study of Evolution (SSE)\\

2020--2021 &  \textbf{Graduate Studies Committee} Department of EEOB, The Ohio State University, OH., USA\\
2019--2020 &	\textbf{Admissions Committee} Department of EEOB, The Ohio State University, OH., USA\\
2016--2017 &	\textbf{Communication Officer} Society for Conservation Biology (SCB), Korean Chapter\vspace{10pt}\\
\end{longtable}





\subsection*{Work Experience}
\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}
2018--Present & \textbf{Graduate Associate} The Ohio State University, OH., USA\\
2016--2017 & \textbf{Researcher} Ewha Womans University, Division of Eco-science, Seoul, South Korea\\%with Dr. Yikweon Jang, 
2013--2015 & \textbf{Graduate Associate} University of Toronto, ON., Canada\\
2011--2013 &	\textbf{Biodiversity Technician} Faculty of Forestry, University of Toronto, ON., Canada\\% with Dr. Sandy Smith and Eric Davies, Urban Biodiversity and Forestry Laboratory
2011&	\textbf{Work-Study Student} Faculty of Forestry, University of Toronto, ON., Canada\vspace{10pt}\\%Wildlife Ecology Laboratory
\end{longtable}





\subsection*{Laboratory Experience}
\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}
2013 &	Ewha Womans University, Division of Eco-science with Dr. Jae Chun Choe, Seoul, South Korea\\%\textbf{Researcher}
2012 &	Centre for Biodiversity and Conservation Biology, Royal Ontario Museum, Toronto, ON., Canada\\
2011--2012 &	McLennan Laboratory, University of Toronto, Toronto, ON., Canada\vspace{10pt}\\
\end{longtable}


\subsection*{Fieldwork Experience}
\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}
2017 & Field expeditions to South Korea, Mongolia, and China (Resulted in publications \#4, 5, and 6)\\
2016 & Field expeditions to Indonesia, Laos, and South Korea (Resulted in publication \#2)\\
2011--2013 & Fieldworks in Greater Toronto Area (GTA), Urban Biodiversity and Forestry Laboratory, University of Toronto, Canada\\
2010 & Fieldworks in GTA, Cities Centre, University of Toronto, Canada\vspace{10pt}\\%\textbf{Field Research Assistant} 
\end{longtable}


\subsection*{Students Advising}
$^\ddag$Undergraduate
\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}
2020 Summer & Shelby Jansens$^\ddag$ and Kimberly Wiles$^\ddag$, co-advised with Dr. Laura Kubatko, Mathematical Biosciences Institute Research Experiences for Undergraduates program. ``Detecting shifts in the evolutionary process in SARS-CoV-2 genomes" \\
2014--2015  & Tulio Soares$^\ddag$ and Ellen Southam$^\ddag$, co-advised with Dr. Pedro Bernardo, University of Toronto and Royal Ontario Museum\\%. \textit{On the use of Median-Joining Networks: A philosophical and empirical evaluation of its suitability in evolutionary biology.}\\
2014 Summer & Shreeram Senthivasan$^\ddag$, co-advised with Drs. Pedro Bernardo, Santiago Sánchez-Pacheco, and Robert Murphy, University of Toronto and Royal Ontario Museum\vspace{10pt}\\%, University of Toronto and Royal Ontario Museum. \textit{Matrilineal relationships of green pitvipers with the description of a new species of the genus} Trimeresurus \textit{(Squamata: Viperidae: Crotalinae) from the central highlands of Vietnam.}
\end{longtable}



\subsection*{Conference/Workshop Participation}
\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}
2021 & Annual Conference of the Korean Association of Biological Sciences, Ewha Womans University, South Korea, virtual\\

2021 & iEvoBio, Evolution Meeting, virtual\\
2021 & \textbf{Chair/Moderator} in multiple Faux-Live Sessions, Evolution Meeting, virtual\\
2021& \textbf{Moderator} International Mixer, Evolution Meeting, virtual\\
2021& \textbf{Moderator} Decolonizing Evolution Workshop, Evolution Meeting, virtual\\
2021 & Workshop in Mathematical and Computational Biology, virtual\\
2021 & SMRT Leiden 2021 – Young Investigator Virtual Conference, hosted by Pacific Biosciences and Leiden University Medical Center, virtual\\
2021 & Transformative Justice within Academia: A radical institutional reflection, The Centre for Criminology and Sociolegal Studies Graduate Student Conference, University of Toronto, virtual\\
2021 & Preparing Future Faculty Zoom Workshop, Workshop \#1: From Graduate School to Full Professor: The Road Less Traveled, The Ohio State University, virtual\\
2021 & Virtual Asilomar 2021, American Society of Naturalists, virtual\\
2020 &	\textbf{Moderator} Strategies for Responding to Harassment and Bullying: Improving Workplace Climate, Evolution Community Resources for Early Career Researchers 2020 (ECR$^2$), virtual\\
2020 &	\textbf{Moderator} Fireside ECR Chat, ECR$^2$, virtual\\
2020 & Future of Systematics Workshop, SSB Meeting, funded by NSF, hosted by Dr. Emily Sessa, University of Florida, Gainesville, FL., USA\\
2020 & SSB Standalone Meeting, Gainesville, FL., USA\\
2019 & Evolution Meeting, Providence, RI., USA\\
2019 & Midwest Phylogenetics Workshop, Itasca Biological Station, funded by NSF, hosted by Dr. Emma Goldberg, University of Minnesota, MN., USA\\
2017 & Annual Conference of the Korean Association of Biological Sciences, Yong-In, South Korea\\
2017 & SCB Asia Section Workshop on Conservation policy, funded by SCB, Bangkok, Thailand\\
2016 & World Congress of Herpetology, Hangzhou and Tonglu, China\\
2015 & Phylogenomics Symposium and Software School, funded by NSF, hosted by Dr. Tandy Warnow, University of Illinois at Urbana-Champaign and University of Michigan, Ann Arbor, MI., USA\\
2015 & SSB Standalone Meeting, University of Michigan, Ann Arbor, MI., USA\vspace{10pt}\\
\end{longtable}


\subsection*{Outreach}
\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}
2019--Present & \textbf{Mentor} Department of EEOB Graduate Mentoring, The Ohio State University, OH., USA (Mentee: McKenna Molnar (2020-2021))\\
2020--Present& \textbf{Mentor} Graduate Student Mentorship Initiative Mentor, Científico Latino\\
2020 &	\textbf{Invited Panelist} EEOB 8894: EEOB Graduate Seminar, The Ohio State University, virtual\\
2020 &	\textbf{Invited Guest} Translational Data Analytics Institute Kickoff Event, College of Arts and Sciences, The Ohio State University, Columbus, OH., USA\\
2019 & \textbf{Volunteer} Museum of Biological Diversity’s Open House, The Ohio State University, OH., USA\\
2016 &  \textbf{Volunteer Biologist} Kuang Si Butterfly Park, Ban Thapene, Luang Prabang District, Laos\vspace{10pt}\\
\end{longtable}


\subsection*{Skills}
\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}
Programming & UNIX, R, Python, Julia\\
Typesetting &  {\LaTeX} and Overleaf, R Markdown, Jupyter Notebook\\
OS & Mac OS X, Windows\\
Others & Geneious Prime, Adobe Illustrator, Microsoft Offices, iWorks, iMovie\\
Languages & Korean (Native), English (Native), Japanese (Intermediate)\vspace{10pt}\\
\end{longtable}



\hspace{0pt}



\section*{Grants and Awards}

\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}% p{0.05\textwidth}
2021 &	EEOB Darwin Talk Society Membership Grant, The Ohio State University\\
2021 &	EEOB Graduate Development Grant, The Ohio State University\\
2020 &	SSE Graduate Research Excellence Grant – R.C. Lewontin Award competition\\% & \$1800
2020 &	NSF Grant for participation in Future of Systematics Workshop, SSB Standalone Meeting\\
2019 &	NSF Grant for participation in Midwest Phylogenetics Workshop\\
2019 &	EEOB Graduate Development Grant, The Ohio State University\\
2017 &	Major contribution to successful grant application to 	National Research Foundation of Korea (2-2017-0410-001-1) PI: Dr. Yikweon Jang, Ewha Womans University, Seoul, South Korea \\%300,000--500,000
2013--2015 & University of Toronto Graduate Fellowship\\
2014 &	E.M. Walker Graduate Award in Biodiversity, University of Toronto\\% & \$2615
2010--2012 &	University of Toronto Undergraduate Bursaries\\% & Funded

\end{longtable}


\hspace{0pt}



\section*{Teaching Experiences}

\subsection*{Teaching Assistantship}

\textit{The Ohio State University}\\
\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}

2021 Summer & \textit{EEOB 2520} Human Physiology\\
2021 Spring & \textit{EEOB 3310} Evolution\\
2020 Fall & \textit{EEOB 3310} Evolution\\
2020 Summer & \textit{EEOB 3310} Evolution\\
2020 Spring & \textit{EEOB 3310} Evolution\\
2019 Fall & \textit{EEOB 3310} Evolution\\
2019 Summer & \textit{EEOB 1930} Introduction to Biological Studies--Aquatic Biology\\
2019 Spring & \textit{EEOB 3310} Evolution\\
2018 Fall & \textit{BIOL 1113} Energy Transformation and Development\\
\end{longtable}


\textit{University of Toronto}\\
\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}

2015 Summer  & \textit{BIO 120} Adaptation and Biodiversity\\
2015 Spring & \textit{BIO 220} From Genomics to Ecosystems in a Changing World\\
2014 Fall & \textit{EEB 362} Macroevolution\\
2014 Summer & \textit{BIO 120} Adaptation and Biodiversity\\
2014 Spring & \textit{EEB 386} Avian Biology\\
2013 Fall & \textit{BIO 120} Adaptation and Biodiversity\\

\end{longtable}

\textit{Miscellaneous}\\
\begin{longtable}{p{0.15\textwidth}  p{0.85\textwidth}}
2016 Spring & Daruma Eco-Farm, Bang Phra, Si Racha District, Chon Buri, Thailand\\
2009 Summer & Cheong-Shim International English Camp, Ga-Pyeong, South Korea\\
\end{longtable}

\hspace{0pt}


\section*{References}

\begin{enumerate}

\item Prof. Dr. Laura S. Kubatko\\
Department of Statistics,\\
Department of Evolution, Ecology, and Organismal Biology\\
The Ohio State University,\\
219 Cockins Hall,\\
Columbus, OH., 43210, USA\\
\href{lkubatko@stat.osu.edu}lkubatko@stat.osu.edu\\
+1 614-247-8846\\

\item Prof. Dr. Bryan C. Carstens\\
Department of Evolution, Ecology, and Organismal Biology\\
The Ohio State University,\\
Museum of Biological Diversity Tetrapod Division, \\
1315 Kinnear Road, \\
Columbus, OH., 43212, USA\\ 
\href{carstens.12@osu.edu}carstens.12@osu.edu\\
+1 614-292-6587\\

\item Prof. Dr. Robert W. Murphy\\
Sr. Curator, Herpetology\\
Centre for Biodiversity and Conservation Biology\\
Department of Natural History-Royal Ontario Museum\\
And Professor of Ecology and Evolutionary Biology\\ 
University of Toronto\\
100 Queen’s Park,\\
Toronto, ON., M3S 2C6, Canada\\
\href{bob.murphy@utoronto.ca}bob.murphy@utoronto.ca\\
+1 416-586-8099

\item Prof. Dr. Deborah A. Mclennan\\
Department of Ecology and Evolutionary Biology\\
University of Toronto\\
25 Harbord St.,\\
Toronto, ON., M5S 3G5, Canada \\
\href{deborah.mclennan@utoronto.ca}deborah.mclennan@utoronto.ca
\\+1 416-978-8538



\end{enumerate}









%-------------------------------------------
\end{document}