%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,letterpaper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{banking} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage{etaremune}

\renewcommand{\labelenumi}{\textbf{[\theenumi]}}   %%<------------------- this

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Sungsik} % Your first name
\familyname{Kong} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Curriculum Vitæ}
\address{Department of Evolution, Ecology, and Organismal Biology -- The Ohio State University}{318 W. 12th Ave., 300 Aronoff Laboratory, Columbus, OH. 43210, USA}
%\mobile{(302) 584 3464}
\phone{614 271 7149}
%\fax{(000) 111 1113}
\email{sungsik.kong@gmail.com}
%\homepage{staff.org.edu/~jsmith}{} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
\extrainfo{sungsik-kong.github.io}
%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{"A witty and playful quotation" - John Smith}

%----------------------------------------------------------------------------------------

\begin{document}
\makecvtitle % Print the CV title
%----------------------------------------------------------------------------------------
%	SECTION
%----------------------------------------------------------------------------------------
%Publications--peer-reviewed; submittted;preprints
%Fellowships and awards
%Teaching and mentoring
%presentations
%professtional development
%outreach/service
%----------------------------------------------------------------------------------------
%\section{Personal Information}
%\textbf{Born:} February 3rd, 1987 in Seoul, South Korea\\
%\textbf{Nationality:} Canada

%----------------------------------------------------------------------------------------
\section{Summary}
$\bullet{}$ Ph.D. in Evolution, Ecology, and Organismal Biology (EEOB), The Ohio State University\\
$\bullet{}$ Presidential Fellow, The Ohio State University\\
$\bullet{}$ Research focus: Phylogenetic methods, computational biology\\

%----------------------------------------------------------------------------------------
\section{Professional Experience}
\textbf{Department of Electrical and Computer Engineering  \hfill 2023--Present}\\
\textit{University of California San Diego, CA., USA \hfill Postdoctoral Scholar}\\
Mentors: Profs. Drs. Siavash Mir Arabbaygi and Vineet Bafna

%----------------------------------------------------------------------------------------
\section{Education}
\textbf{Ph.D. in Evolution, Ecology, and Organismal Biology \hfill 2018--2022}\\
\textit{The Ohio State University, Columbus, OH., USA}\\
Dissertation: Towards the network of life: Phylogenetic networks as a tool to understand complex evolutionary histories\\
Advisor: Prof. Dr. Laura Kubatko\\

\textbf{M.Sc. in Ecology and Evolutionary Biology \hfill 2013--2015}\\
\textit{University of Toronto, Toronto, ON., Canada}\\
Thesis: On the use of Median-Joining networks: A philosophical and empirical evaluation of its suitability in evolutionary biology\\
Advisor: Prof. Dr. Robert Murphy\\

\textbf{B.Sc. in Zoology and Ecology and Evolutionary Biology \hfill 2006--2012}\\
\textit{University of Toronto, Toronto, ON., Canada}
%Undergraduate Thesis Advisors: Profs. Drs. Robert Murphy and Deborah McLennan\\
\pagebreak

%----------------------------------------------------------------------------------------
\section{Publications}
\textbf{Total number:} 16\\
\textbf{h-index:} 7 \href{https://scholar.google.com/citations?user=UQFcoZoAAAAJ&hl=en}{[Google scholar]}\\

\subsection{Peer-reviewed journal articles}
$^\ddag$Co-correspondence; $^\dag$Equal contribution
\begin{etaremune}
	\item Glon H, Häussermann V, Brewin P, Brickle P, \textbf{Kong S}, Smith M, and Daly M. (In Press) There and back again: The unexpected journeys of \textit{Metridium} de Blainville, 1824 between the old oceans and throughout the modern world. \textit{Biological Bulletin}
	
	\item Nguyen HQ, Ho P-T, \textbf{Kong S}, Bae Y, Pham TH, and Jang Y. (2022) A time-calibrated mitogenomic phylogeny suggests that Korean \textit{Hyalessa fuscata} is a bridge between Chinese and Japanese \textit{H. maculaticollis}. \textit{Journal of Genetics} 102:9 doi:\href{https://doi.org/10.1007/s12041-022-01405-7}{10.1007/s12041-022-01405-7}
	
	\item \textbf{Kong S} (2022) Digest: Frequent hybridization in \textit{Darevskia} rarely leads to the evolution of asexuality. \textit{Evolution} 76:9 2216--2217 doi:\href{https://doi.org/10.1111/evo.14587}{10.1111/evo.14587}
	
	\item Nguyen HQ, Kim E, Bae Y, Chae S, Ji S, Heo J, \textbf{Kong S}, Nguyen TK, Pham TH, and Jang Y. (2022) An effective method for accurate life-stage delimitation of cicadas. \textit{Journal of Asia-Pacific Entomology} 101952 doi:\href{https://doi.org/10.1016/j.aspen.2022.101952}{10.1016/j.aspen.2022.101952}
	
	\item \textbf{Kong S}$^\dag$, Pons JC$^\dag$, Kubatko LS, and Wicke K. (2022) Classes of phylogenetic networks and their mathematical and biological significance. \textit{Journal of Mathematical Biology} 84:47 doi:\href{https://doi.org/10.1007/s00285-022-01746-y}{10.1007/s00285-022-01746-y}
	
	\item Glon MG, Broe MB, Crandall KA, Daly M, \textbf{Kong S}, Thoma RF, and Freudenstein JV. (2022) Anchored hybrid enrichment resolves the \textit{Lacunicambarus} (Decapoda: Cambaridae) phylogeny. \textit{Journal of Crustacean Biology} 42:1 ruab073 doi:\href{https://doi.org/10.1093/jcbiol/ruab073}{10.1093/jcbiol/ruab073}
	
	\item \textbf{Kong S} and Kubatko LS. (2021) Comparative performance of popular methods for hybrid detection using genomic data. \textit {Systematic Biology} 70:5 891–907 doi:\href{https://doi.org/10.1093/sysbio/syaa092}{10.1093/sysbio/syaa092}
	
	\item  Sánchez-Pacheco SJ{$^\ddag$}, \textbf{Kong S}{$^\ddag$}, Pulido-Santacruz P, Murphy RW, and Kubatko L. (2020) Median-joining network analysis of SARS-CoV-2 genomes is neither phylogenetic nor evolutionary. \textit{Proc. Natl. Acad. Sci. U.S.A} 117:23 12518–12519 doi:\href{https://doi.org/10.1073/pnas.2007062117}{10.1073/pnas.2007062117}
	
	\item Kim M, Nguyen HQ, Yi Y, Ahn J, Kim YE, Jang S, Kim S, \textbf{Kong S}, and Borzée A. (2020) Policy recommendation on whaling, trade and watching of cetaceans in the Republic of Korea. \textit{Biodiversity Journal} 11: 255–258 doi:\href{https://doi.org/10.31396/Biodiv.Jour.2020.11.1.255.258}{10.31396/Biodiv.Jour.2020.11.1.255.258}

\pagebreak
	\item Weiringa JG, Boot MR,  Dantas-Queiroz MV, Duckett D, Fonseca EM, Glon H, Hamilton N, \textbf{Kong S}, Lanna FM, Mattingly KZ, Parsons DJ, Smith ML, Stone BW, Thompson C, Zuo L, and Carstens BC. (2020) Does habitat stability structure intraspecific genetic diversity? It’s complicated… \textit{Frontiers in Biogeography} e45377 doi:\href{https://doi.org/10.21425/F5FBG45377}{10.21425/F5FBG45377}
	
	\item Borzée A, Purevdorj Z, Kim YI, \textbf{Kong S}, Choe M, Yi Y, Kim K, Kim A, and Jang Y. (2020) Breeding preferences in the Treefrogs \textit{Dryophytes japonicus} (Hylidae) in Mongolia, the northern limit of their range. \textit{Journal of Natural History} 53: 2685-2698 doi:\href{https://doi.org/10.1080/00222933.2019.1704458}{10.1080/00222933.2019.1704458}
	
	\item Groffen J, \textbf{Kong S}, Jang Y, and Borzée A. (2019) The invasive American bullfrog (\textit{Lithobates catesbeianus}) in the Republic of Korea: history and recommendation for population control. \textit{Management of Biological Invasions} 10:3 517–535 doi:\href{https://doi.org/10.3391/mbi.2019.10.3.08}{10.3391/mbi.2019.10.3.08}
	
	\item Bae Y, \textbf{Kong S}, Yi Y, Jang Y, and Borzée A. (2019) Additional new type of threat to \textit{Hynobius} salamander eggs: predation by loaches (\textit{Misgurnus} sp.) in agricultural wetlands. \textit{Animal Biology} 69:4 451–461 doi:\href{https://doi.org/10.1163/15707563-20191070}{10.1163/15707563-20191070}
	
	\item Borzée A,\textbf{ Kong S}, Didinger C, Nguyen HQ, and Jang Y. (2018) A ring-species or a ring of species? Phylogenetic relationship between two treefrog species around the Yellow Sea: \textit{Dryophytes suweonensis} and \textit{D. immaculatus}. \textit{The Herpetological Journal} 28: 160–170 
	
	\item Kim K, \textbf{Kong S}, Kim YI, Borzée A, Bae Y, and Jang Y. (2018) Japanese hard ticks (\textit{Ixodes nipponensis}) parasitizing on the endangered leopard cat (\textit{Prionaliurus bengalensis euptilura}) in the Republic of Korea. \textit{Animal Systematics, Evolution and Diversity} 34:1 23–26 doi:\href{https://doi.org/10.5635/ASED.2018.34.1.032}{10.5635/ASED.2018.34.1.032}
	
	\item \textbf{Kong S}{$^\dag$}, Sánchez-Pacheco S{$^\dag$}, and Murphy RW. (2016) On the use of Median-Joining Networks in evolutionary biology. \textit{Cladistics} 32: 691–699 doi:\href{https://doi.org/10.1111/cla.12147}{10.1111/cla.12147}
\end{etaremune}

\subsection{Policy recommendations}
\begin{etaremune}
	\item Borzée A, Nguyen HQ, Ahn J, Kim M, Kim S, Jang S, \textbf{Kong S}, Kim YE, and Yi Y. (2017) Policy recommendation on the negative impact of infrastructure development on the population of endangered Long-Tailed Goral in Oseck-Kkeutchong. \textit{Society for Conservation Biology Korean Chapter}
\end{etaremune}

\subsection{Submitted}
\begin{etaremune}
	\item \textbf{Kong S}, Swofford DL, and Kubatko LS. (In Review) Inference of phylogenetic networks from sequence data using composite likelihood. Preprint available on \textit{bioRxiv} at \href{https://www.biorxiv.org/content/10.1101/2022.11.14.516468v1}{10.1101/2022.11.14.516468v1}%Syst Biol
	\item \textbf{Kong S}, Sánchez-Pacheco SJ, and Murphy RW. (In Review) Topological incongruence between median-joining networks and Bayesian inference phylogenies. Preprint available on \textit{bioRxiv} at \href{https://doi.org/10.1101/2022.10.01.510440}{10.1101/2022.10.01.510440}%BSSB
	\item Fu M, Eimes JA, \textbf{Kong S}, Lamichhaney S, and Waldman B. (In Review) Chytrid-resistant genotypes arise from multiple mutations. 	
\end{etaremune}

%----------------------------------------------------------------------------------------
\pagebreak
\section{Presentations}
$^\star$Virtual presentation
\subsection{Invited talks}
\begin{etaremune}
	\item \textbf{Algorithms and Complexity in Phylogenetics$^\star$ \hfill 2022}\\
		{\small Title: Inferring phylogenetic networks from sequence data using composite likelihood\\
		Video recording available on YouTube \href{https://www.youtube.com/watch?v=t6Ta-0Wz1ys&t=1915s}{[link]}}

	\item \textbf{Indiana University, Bloomington, IN., USA \hfill 2022}\\
		{\small \textit{Dr. Matthew Hahn laboratory}\\
		Title: Towards the Network of Life: Phylogenetic networks as a tool to understand complex evolutionary histories}
		
	\item \textbf{University of California San Diego, CA., USA$^\star$ \hfill 2022}\\
		{\small \textit{Drs. Siavash Mir Arabbaygi and Vineet Bafna laboratory}\\
		Title: Towards the Network of Life: Phylogenetic networks as a tool to understand complex evolutionary histories}
		
	\item \textbf{Evolution Meeting, Cleveland, OH., USA \hfill 2022}\\
		{\small \textit{Society of Systematic Biologists (SSB) Ernst Mayr award competition}\\
		Title: Inferring phylogenetic networks using composite likelihood directly from sequence data}
		
	\item \textbf{Louisiana State University, Baton Rouge, LA., USA \hfill 2022}\\
		{\small \textit{Dr. Jeremy Brown laboratory and Department of Biological Sciences}\\
		Title: Inferring phylogenetic networks using composite likelihood directly from sequence data}
		
	\item \textbf{The Korean Association of Biological Sciences, Seoul, South Korea$^\star$ \hfill 2021}\\
		{\small \textit{The Ecological Society of Korea Section}\\
		Title: Comparative performance of popular methods for hybrid detection using genomic data}
		
	\item \textbf{Workshop in Mathematical and Computational Biology$^\star$ \hfill 2021}\\
		{\small \textit{Bioinformatics Section}\\
		Title: Comparative performance of popular methods for hybrid detection using genomic data}

	\item \textbf{Misericordia University, Dallas, PA., USA$^\star$ \hfill 2021}\\
		{\small \textit{Biology Seminar Series}\\
		Title: How my gap year changed my perspectives}

	\item \textbf{The Stone Laboratory, Gibraltar Island, OH., USA \hfill 2019}\\
		{\small \textit{EEOB 1930 Introduction to Biological Studies--Aquatic Biology}\\
		Title: Phylogenetic networks and behavioral evolution of Primates}

	\item \textbf{Ewha Womans University, Seoul, South Korea \hfill 2016}\\
		{\small \textit{Eco-science/Eco-creative Graduate Seminar}\\
		Title: On the use of Median-Joining network}

	\item \textbf{Ewha Womans University, Seoul, South Korea \hfill 2013}\\
		{\small \textit{Laboratory of Behavior and Ecology Weekly Seminar}\\
		Title: The evolution of infanticide and male takeover in primates in a macroevolutionary framework}
\end{etaremune}

\subsection{Regular talks}
\begin{etaremune}
	\item \textbf{Evolution Meeting$^\star$ \hfill 2021}\\
		{\small Title: Comparative performance of popular methods for hybrid detection using genomic data}

	\item \textbf{The Ohio State University, Columbus, OH., USA$^\star$ \hfill 2021}\\
		{\small \textit{EEOB Annual Darwin Series}\\
		Title: Comparative performance of popular methods for hybrid detection using genomic data}

	\item \textbf{The Ohio State University, Columbus, OH., USA \hfill 2020}\\
		{\small \textit{Evolution \& Ecology Club}\\
		Title: Which tool to use to detect hybridization?}

	\item \textbf{SSB Standalone Meeting, Gainesville, FL., USA \hfill 2020}\\
		{\small Title: Comparison and evaluation on the accuracy of popular hybrid detection methods using simulated data}

	\item \textbf{The Ohio State University, Columbus, OH., USA \hfill 2019}\\
		{\small \textit{Evolution \& Ecology Club}\\
		Title: The giving tree: how the branching pattern of a tree is used in evolutionary biology}

	\item \textbf{Ewha Womans University, Seoul, South Korea \hfill 2017}\\
		{\small \textit{Animal Communication Symposium}\\
		Title: Illustrating hybridization}
\end{etaremune}

\subsection{Poster presentations}
\begin{etaremune}
	\item \textbf{Intelligent Systems for Molecular Biology (ISMB), \hfill 2022}\\ \textbf{The International Society for Computational Biology (ISCB), Madison, WI., USA}\\
		{\small{\color{red}{\textit{Best Poster Award Winner}}}\\
		Title: Inference of phylogenetic networks from sequence data using composite likelihood}

	\item \textbf{Evolution Meeting, Providence, RI., USA \hfill 2019}\\
		{\small Title: Performance and accuracy of Median-Joining Networks and comparisons with Bayesian phylogenies}

	\item \textbf{The Korean Association of Biological Sciences, Yong-In, South Korea \hfill 2017}\\
		{\small Title: Performance and accuracy of Median-Joining Networks and comparisons with Bayesian phylogenies}
		  		  
	\item \textbf{Korean-American Scientists and Engineers Association (KSEA) \hfill{2014}\\
	Young Generation Technical and Leadership Conference (YGTLC), Houston, TX., USA}\\
		{\small Title: Matrilineal relationships of green pitvipers with the description of a new species of the genus \textit{Trimeresurus} (Squamata: Viperidae: Crotalinae) from the central highlands of Vietnam}
	
		\item \textbf{University of Toronto, Toronto, ON., Canada \hfill 2012}\\
		{\small \textit{Department of Ecology and Evolutionary Biology undergraduate research Fair}\\
		Title: The evolution of infanticide and male takeover in primates in a macro- evolutionary framework}
\end{etaremune}
%	\item EEOB Recruitment Speed Talk, The Ohio State University, OH., USA, virtual \hfill 2021, 2022
%	\item 2019   EEOB Recruitment Weekend,  The Ohio State University, OH., USA \\

%----------------------------------------------------------------------------------------
\pagebreak
\section{Academic Experience}
\textbf{University of Wisconsin--Madison, WI., USA  \hfill{2022}}\\ 
\textit{Wisconsin Institute for Discovery \hfill {Visiting Ph.D. student}}\\
Mentor: Prof. Dr. Claudia Solís-Lemus\\

\textbf{Louisiana State University, Baton Rouge, LA., USA \hfill{2022}}\\
\textit{Department of Biological Sciences  \hfill Visiting Ph.D. student}\\
Mentor: Prof. Dr. Jeremy Brown\\

\textbf{The Ohio State University, Columbus, OH., USA \hfill 2018--2021}\\
\textit{Department of Evolution, Ecology, and Organismal Biology \hfill Graduate associate}\\

\textbf{Ewha Womans University, Seoul, South Korea \hfill{2016--2017}}\\
\textit{Division of Eco-science \hfill Researcher}\\
Mentor: Prof. Dr. Yikweon Jang\\

\textbf{University of Toronto, ON., Canada \hfill{2013--2015}}\\
\textit{Department of Ecology and Evolutionary Biology  \hfill Graduate associate}\\

\textbf{Ewha Womans University, Seoul, South Korea \hfill{2013}}\\
\textit{Division of Eco-science \hfill Student researcher}\\
Mentor: Prof. Dr. Jae Chun Choe\\

\textbf{University of Toronto, ON., Canada \hfill{2011--2013}}\\
\textit{Faculty of Forestry \hfill Work-Study student}\\
Mentor: Prof. Dr. Sandy Smith and Eric Davies \textit{\hfill Biodiversity technician}\\

\textbf{Royal Ontario Museum, Toronto, ON., Canada \hfill{2012}}\\
\textit{Centre for Biodiversity and Conservation Biology \hfill Student researcher}\\
Mentor: Prof. Dr. Robert Murphy\\

\textbf{University of Toronto, ON., Canada \hfill{2011--2012}}\\
\textit{Department of Ecology and Evolutionary Biology \hfill Student researcher}\\
Mentor: Prof. Dr. Deborah McLennan\\

\textbf{University of Toronto, ON., Canada \hfill{2010}}\\
\textit{Cities Centre, Department of Geography \hfill Student data collector}\\
%Mentor: Dr. Kristian Larsen\\

\subsection{Fieldwork experience}
\begin{itemize}		
	\item South Korea, Mongolia, and China \hfill{\textbf{2017}}
	\item Indonesia, Laos, and South Korea \hfill{\textbf{2016}}
	\item Greater Toronto Area (GTA) \hfill{\textbf{2010--2013}}
\end{itemize}		

%----------------------------------------------------------------------------------------
\pagebreak
\section{Teaching and Mentoring Experience}
\subsection{The Ohio State University}
	\textit{Teaching assistant}
\begin{itemize} 
	\item \textit{EEOB 3310} Evolution \hfill (Spring, Fall) 2021\\ 
				\indent\hfill (Spring, Summer, Fall) 2020\\ 
				\indent\hfill (Spring, Fall) 2019
	\item \textit{EEOB 2520} Human Physiology \hfill (Summer) 2021
	\item \textit{EEOB 1930} Introduction to Biological Studies--Aquatic Biology \hfill (Summer) 2019
	\item \textit{BIOL 1113} Energy Transformation and Development \hfill (Fall) 2018
\end{itemize} 

\subsection{University of Toronto}
	\textit{Teaching assistant}
\begin{itemize} 
	\item \textit{BIO 120} Adaptation and Biodiversity \hfill (Summer) 2015\\
				\indent\hfill (Summer) 2014\\
				\indent\hfill (Fall) 2013
	\item \textit{BIO 220} From Genomics to Ecosystems in a Changing World \hfill (Spring) 2015
	\item \textit{EEB 362} Macroevolution \hfill (Fall) 2014
	\item \textit{EEB 386} Avian Biology \hfill (Spring) 2014
\end{itemize} 

\subsection{Miscellaneous}
\begin{itemize} 
	\item Daruma Eco-Farm, Bang Phra, Si Racha District, Chon Buri, Thailand \hfill 2016
	\item Cheong-Shim International English Camp, Ga-Pyeong, South Korea \hfill 2009
\end{itemize}

\subsection{(Co-)supervision of undergraduate students}
\begin{itemize}
	\item Alanna Kong \hfill{2021--2022}\\
	\textit{\small Undergraduate student at University of Toronto\\
	University of Toronto Woodsworth Mentorship Program}
	
	\item Devansh Pandey \hfill{2021--2022}\\
	\textit{\small Undergraduate student at Indian Institute of Technology Kharagpur,\\
	Current graduate student at University of Texas at Austin\\
	Científico Latino}
	
	\item McKenna Molnar \hfill{2020-2021}\\
	\textit{\small Graduate student at The Ohio State University\\
	EEOB Graduate Mentoring Program, The Ohio State University, OH., USA}
	
	\item Shelby Jansens and Kimberly Wiles \hfill{2020}\\
	 {\small \textit{Co-supervised with Dr. Laura Kubatko\\
	 Mathematical Biosciences Institute Research Experiences for Undergraduates program}\\
	 Title: Detecting shifts in the evolutionary process in SARS-CoV-2 genomes}
	
	\item Tulio Soares and Ellen Southam \hfill 2014--2015\\
	\textit{\small Co-supervised with Dr. Pedro Bernardo\\
	University of Toronto and Royal Ontario Museum}
	
	\item Shreeram Senthivasan \hfill {2014}\\
	\textit{\small Co-supervised with Drs. Pedro Bernardo, Santiago Sánchez-Pacheco, and Robert Murphy\\
	 University of Toronto and Royal Ontario Museum}
\end{itemize}

\section{Conference and Workshop Participation}
\textit{$^\star$Virtual event\\
Bolds state particular role in the event; participant if unstated} 
\vspace{-0.25cm}\\
\begin{itemize}
	\item \textbf{Technical Moderator}  \hfill{2022}\\
	ISMB, ISCB, Madison, WI., USA
	
%	\item Evolution Meeting, Cleveland, OH., USA \hfill{2022}
	\item \textbf{Symposium Organizer (co-organized with Md Rejuan Haque) } \hfill{2022}\\
	Evolution Meeting, Cleveland, OH., USA\\
	{\small \textit{Symposium title: Towards the network of life: Phylogenetic networks as a tool to understand complex evolutionary histories.}}
	
	\item Workshop in Mathematical and Computational Biology$^\star$ \hfill{2022}
	
	\item Annual Conference of the Korean Association of Biological Sciences, South Korea$^\star$ \hfill{2021}	
	
	\item iEvoBio (Informatics for Phylogenetics, Evolution and Biodiversity), Evolution Meeting$^\star$ \hfill{2021}
	
	\item \textbf{Chair/Moderator} in multiple Faux-Live Sessions, Evolution Meeting$^\star$ \hfill{2021}
	
	\item Workshop in Mathematical and Computational Biology$^\star$ \hfill{2021}	
	
	\item SMRT Leiden 2021 – Young Investigator Virtual Conference, hosted by Pacific Biosciences and Leiden University Medical Center$^\star$ \hfill{2021}	
	
%	\item Preparing Future Faculty Zoom Workshop, Workshop \#1: From Graduate School to Full Professor: The Road Less Traveled, The Ohio State University$^\star$ \hfill{2021}	

	\item Virtual Asilomar 2021, American Society of Naturalists$^\star$ \hfill{2021}	

	\item Future of Systematics Workshop, SSB Standalone Meeting, funded by NSF, hosted by Dr. Emily Sessa, University of Florida, Gainesville, FL., USA \hfill{2020}

	\item SSB Standalone Meeting, Gainesville, FL., USA \hfill{2020}

	\item Evolution Meeting, Providence, RI., USA \hfill{2019}

	\item Midwest Phylogenetics Workshop, Itasca Biological Station, funded by NSF, hosted by Dr. Emma Goldberg, University of Minnesota, MN., USA \hfill{2019}

	\item Annual Conference of the Korean Association of Biological Sciences, Yong-In, South Korea \hfill{2017}

	\item Society for Conservation Biology (SCB) Asia Section Workshop on Conservation policy, funded by SCB, Bangkok, Thailand \hfill{2017}

	\item World Congress of Herpetology, Hangzhou and Tonglu, China \hfill{2016}

	\item Phylogenomics Symposium and Software School, funded by NSF, hosted by Dr. Tandy Warnow, University of Illinois at Urbana-Champaign and University of Michigan, Ann Arbor, MI., USA \hfill{2015}
	
	\item SSB Standalone Meeting, University of Michigan, Ann Arbor, MI., USA \hfill{2015}\\
\end{itemize}

\section{Diversity and Inclusion Activities}
\begin{itemize}
	\item International Mixer, Evolution Meeting, Cleveland, OH., USA \hfill{2022}
	\item \textbf{Moderator} International Mixer, Evolution Meeting$^\star$ \hfill{2021}
	\item \textbf{Moderator} Decolonizing Evolution Workshop, Evolution Meeting$^\star$ \hfill{2021}
	\item Transformative Justice within Academia: A radical institutional reflection, The Centre for Criminology and Sociolegal Studies Graduate Student Conference, University of Toronto$^\star$ \hfill{2021}
	\item \textbf{Moderator} Strategies for Responding to Harassment and Bullying: Improving Workplace Climate, Evolution Community Resources for Early Career Researchers 2020 (ECR$^2$)$^\star$ \hfill{2020}
	\item \textbf{Moderator} Fireside ECR Chat, ECR$^2$$^\star$ \hfill{2020}
\end{itemize}
\section{Grants and Awards}
All in US Dollars unless stated. \dag Canadian Dollar; \ddag Approximately converted from South Korean Won 

\begin{itemize}
	\item 2022 	EvolCompGen Best Poster Award, ISMB, ISCB	\$100
	\item 2022 	EEOB Graduate Development Grant, The Ohio State University	Funded
	\item 2022 	EEOB Graduate Evolution \& Ecology Student Organization (GEES) Career Development Grant, The Ohio State University \$200
	\item 2022  	Council of Graduate Students (CGS) Career Development Grant, The Ohio State University \$350
	\item 2022 	The Presidential Fellowship, The Ohio State University \$36,500
	\item 2021 	SSB Ad Hoc Funds	\$3,000
	\item 2021 	EEOB Darwin Talk Society Membership Grant, The Ohio State University	\$70
	\item 2021 	EEOB Graduate Development Grant, The Ohio State University	Funded
	\item 2020 	SSE Graduate Research Excellence Grant – R.C. Lewontin Award competition	\$1,800
	\item 2020 	Funding for participation in Future of Systematics Workshop, SSB Standalone Meeting (NSF)	\$500
	\item 2019 	Funding for participation in Midwest Phylogenetics Workshop (NSF)	Funded
	\item 2019 	EEOB Graduate Development Grant, The Ohio State University	Funded
	\item 2017 	Major contribution to successful grant application to 	National Research Foundation of Korea (2-2017-0410-001-1) PI: Dr. Yikweon Jang, Ewha Womans University, Seoul, South Korea	 \ddag\$500,000
	\item 2013--2015  University of Toronto Graduate Fellowship	 Funded
	\item 2014 	E.M. Walker Graduate Award in Biodiversity, University of Toronto	\dag\$2,615
	\item 2010--2012 	University of Toronto Undergraduate Bursaries	 \dag$\approx$\$3,000
\end{itemize}


\section{Outreach and Service}
\begin{itemize}


%	\item \textbf{Mentor \hfill{2021--2022}}\\
%	Woodsworth Mentorship Program, University of Toronto, ON., Canada\\
%	Mentee: Alanna Kong, Undergraduate at University of Toronto

%	\item \textbf{Graduate Student Mentorship Initiative Mentor  \hfill{2020--2022}}\\
%	Científico Latino\\
%	Mentee: Devansh Pandey, Undergraduate at Indian Institute of Technology Kharagpur 

%	\item \textbf{Mentor  \hfill{2019--2021}}\\
%	EEOB Graduate Mentoring Program, The Ohio State University, OH., USA\\
%	Mentee: McKenna Molnar, Graduate student at the Ohio State University
	\item \textbf{Awardee} Graduate School Awards Ceremony, The Ohio State University, Columbus, OH., USA \hfill{2022}
	
	\item \textbf{Invited Panelist} EEOB 8894: EEOB Graduate Seminar, The Ohio State University, OH., USA  \hfill{2020}
	
	\item \textbf{Invited Guest} Translational Data Analytics Institute Kickoff Event, College of Arts and Sciences, The Ohio State University, OH., USA \hfill{2020}

	\item \textbf{Volunteer} Museum of Biological Diversity’s Open House, The Ohio State University, OH., USA \hfill{2019}

	\item Graduate Studies Committee Department of EEOB, The Ohio State University, OH., USA \hfill{2020--2021}

	\item Admissions Committee Department of EEOB, The Ohio State University, OH., USA \hfill{2019--2020}

	\item Communication Officer Society for Conservation Biology (SCB), South Korean Chapter \hfill{2016--2017}
	
	\item \textbf{Volunteer Biologist} Kuang Si Butterfly Park, Ban Thapene, Luang Prabang District, Laos \hfill{2016}
\end{itemize}
\section{Peer-Review Activities}%
\begin{itemize}
	\item Systematic Biology
	\item Molecular Biology and Evolution
	\item Genome Biology and Evolution
	\item Scientific Reports
	\item Infection, Genetics and Evolution
\end{itemize}

\section{Professional Memberships}%
\begin{itemize}
	\item Society of Systematic Biologists
	\item Society for Study of Evolution
	\item International Society for Computational Biology
\end{itemize}

\section{Skills}%
\textbf{Programming} UNIX, R, Python, Julia, HTML, JavaScript\\
\textbf{Typesetting} {\LaTeX}, R Markdown, Jupyter Notebook\\
\textbf{Languages} English (Fluent), Korean (Native), Japanese (Intermediate)

\pagebreak
\section{References}
\begin{enumerate}

\item \textbf{Prof. Dr. Laura S. Kubatko (Ph.D. advisor)}\\Department of Statistics and Department of Evolution, Ecology, and Organismal Biology\\The Ohio State University\\219 Cockins Hall, Columbus, OH., 43210, USA\\\href{lkubatko@stat.osu.edu}lkubatko@stat.osu.edu\\+1 614-247-8846\\

\item \textbf{Prof. Dr. Robert W. Murphy (M.Sc. advisor)}\\Department of Natural History-Royal Ontario Museum\\And Professor of Ecology and Evolutionary Biology\\ University of Toronto\\100 Queen’s Park\\Toronto, ON., M3S 2C6, Canada\\\href{bob.murphy@utoronto.ca}bob.murphy@utoronto.ca\\+1 416-586-8099\\

\item \textbf{Prof. Dr. Deborah A. Mclennan (B.Sc. advisor)}\\Department of Ecology and Evolutionary Biology\\University of Toronto,\\25 Harbord St.\\Toronto, ON., M5S 3G5, Canada \\\href{deborah.mclennan@utoronto.ca}deborah.mclennan@utoronto.ca\\+1 416-978-8538\\

\item \textbf{Prof. Dr. Bryan C. Carstens}\\ Department of Evolution, Ecology, and Organismal Biology\\ And Tetrapod Division, Museum of Biological Diversity\\The Ohio State University,\\318 W. 12th Avenue,\\Columbus, OH., 43210, USA\\\href{carstens.12@osu.edu}carstens.12@osu.edu\\+1 614-292-6587\\
% (Ph.D. dissertation committee)}

\item \textbf{Prof. Dr. Jeremy M. Brown}\\ Department of Biological Sciences\\Louisiana State University\\ A243 Life Science Annex,\\ Baton Rouge, LA., 70803, USA\\\href{jembrown@lsu.edu}jembrown@lsu.edu\\ +1 225-578-1745
\end{enumerate}
\end{document}